Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-01-02 paper.tex
review conclusions

Given that software complexity has significantly increased in embedded products, there are still some (recent) advances to stress and exhaustively cover the system state space, in order to verify low-level properties that have to meet the application's deadline, access memory regions, handle concurrency, and control hardware registers. Besides, there is a trend towards incorporating knowledge about the system to be verified, which may take software verification one step further, where not only code correctness will be addressed, but also full system reliability. Finally, it seems interesting to provide behavioral models when new application interfaces or programming language features are used, in order to extend the capabilities of current verification tools, without changing the core BMC module.

As future work, the main goal of this research is to extend BMC as a design and verification tool for achieving correct-by-construction embedded system implementations. Special attention will be given to cyber-physical systems and modern micro-grids, considering small-scale versions of a distributed system, so that reliability and other system-level properties ({\it e.g.}, carbon emission reduction in smart cities) are amenable to automated verification, probably through behavior models.

>>>>

Given that software complexity has significantly increased in embedded products, there are still some (recent) advances to stress and exhaustively cover the system state space, in order to verify low-level properties that have to meet the application's deadline, access memory regions, handle concurrency, and control hardware registers. Besides, there is a trend towards incorporating knowledge about the system to be verified, which may take software verification and synthesis one step further, where not only code correctness will be addressed, but also full system reliability. Finally, it seems interesting to provide behavioral models when new application interfaces or programming language features are used, in order to extend the capabilities of current verification tools, without changing the core BMC module.

As future work, the main goal of this research is to extend BMC as a design, verification, and synthesis tool for achieving correct-by-construction embedded system implementations. Special attention will be given to cyber-physical systems and modern micro-grids, considering small-scale versions of a distributed system, so that reliability and other system-level properties ({\it e.g.}, carbon emission reduction in smart cities) are amenable to automated verification, probably through behavior models.
